### 2019-04-05 papers/journal/encoding.tex
BMC update

\noindent Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
%Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are 
%In $\fbmc$ we only partially unroll the program to check for the solutions within that subset. 
%in the case of $\fbmc$, the encoding is not considerably different.
% 
In comparison to $\fsmt$, the $\fbmc$ search encodes reachability (both for the stability and connectivity) differently.  
%]
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

>>>>

\noindent Our first attempt was to encode the existential condition as a $\fbmc$ search problem~\cite{shukla2017discovering}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
%Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are 
%In $\fbmc$ we only partially unroll the program to check for the solutions within that subset. 
%in the case of $\fbmc$, the encoding is not considerably different.
% 
The main difference between $\fsmt$ and $\fbmc$ is the encoding of 
%I n comparison to $\fsmt$, the $\fbmc$ search encodes 
reachability (both for the stability and connectivity).  
%]
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.
